### 2020-07-31 README.Rmd
upd README with link to spatiotemp viz vignette
add ResamplingSptCVCstf

| Literature                | Package     | Reference     | mlr3 Sugar                     |
| ---------------           | ---------   | ---------     | ---------------                |
| Spatial Buffering         | blockCV     | Valavi 2019   | `rsmp("spcv-buffer")`          |
| Spatial Blocking          | blockCV     | Valavi 2019   | `rsmp("spcv-block")`           |
| Spatial CV                | sperrorest  | Brenning 2012 | `rsmp("spcv-coords")`          |
| Environmental Blocking    | blockCV     | Valavi 2019   | `rsmp("spcv-env")`             |
|           -               | -           | -             | `rsmp("spcv-cluto")`           |
| ---                       | ---         | ---           | ---                            |
| Repeated Spatial Blocking | blockCV     | Valavi 2019   | `rsmp("repeated-spcv-block")`  |
| Repeated Spatial CV       | sperrorest  | Brenning 2012 | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking     | blockCV     | Valavi 2019   | `rsmp("repeated-spcv-env")`    |
|           -               | -           | -             | `rsmp("repeated-spcv-cluto")`  |

@@

>>>>

| Literature                  | Package    | Reference     | mlr3 Sugar                     |
| --------------------------- | ---------- | ------------- | ------------------------------ |
| Spatial Buffering           | blockCV    | Valavi 2019   | `rsmp("spcv-buffer")`          |
| Spatial Blocking            | blockCV    | Valavi 2019   | `rsmp("spcv-block")`           |
| Spatial CV                  | sperrorest | Brenning 2012 | `rsmp("spcv-coords")`          |
| Environmental Blocking      | blockCV    | Valavi 2019   | `rsmp("spcv-env")`             |
| -                           | -          | -             | `rsmp("sptcv-cluto")`          |
| Leave-Location-and-Time-Out | CAST       | Meyer 2018    | `rsmp("sptcv-cstf")`           |
| ---                         | ---        | ---           | ---                            |
| Repeated Spatial Blocking   | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-block")`  |
| Repeated Spatial CV         | sperrorest | Brenning 2012 | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking       | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-env")`    |
| -                           | -          | -             | `rsmp("repeated-sptcv-cluto")` |

@@

(See vignette ["Spatiotemporal Visualization"](https://mlr3spatiotempcv.mlr-org.com/articles/spatiotemp-viz.html) for an interactive 3D HTML variant.)
